### 2022-06-01 rebuttal2.txt

We thank the three reviewers for their thorough reading and
interesting comments.

* About motivation and practical application: (TODO) Add reference to Bastien's paper
A user from Europe wants to download a video indexed only in
Australia despite a neighbor
European having a replica (because he was interested in the video as
well). Still, the former originates a round-trip to Australia only to
discover that it wasted time looking for the location of the video
that was next to him.  DHTs also have this pitfall where nodes knowing
the video locations might be running in Australia. Our approach
proposes a trade-off that allows close node to answer location
requests, even in dynamic networks where nodes can quickly reconfigure
to meet the changes in a peer-to-peer fashion.
** Action: We use such an example throughout the paper, complementing
the figure descriptions with real-world usage and location.
** Side note: Out of the scope of networking, our approach also
constitutes an efficient way to perform a multi-destinations shortest
path in dynamic graphs.

* About failure detection: We agree with Reviewer 2 that implementing
link failure detection is often done using heartbeats. Our approach is
built on top of such links and benefits, as many other running
protocols, from such failure detection. Since this is a shared overhead,
we do not account it as being part of our protocol.
** Action: Clarify this prerequisite and its implication on the overhead.

* About crash recovery: As of now, crashes may have immediate impact
on neighboring nodes depending on their crash detection
speed. Therefore, a node must always restart anew, thus retrieving and
propagating relevant information again.
** Side note: There exists a trade-off between convergence speed and
and generated traffic when buffering incoming messages and only
propagating most relevant ones. We kept this out of scope for the
sake of simplicity.

* About the experiments: PeerSim, despite being old, remains a
flexible framework to run large scale simulations. It fits our goal of
isolating the behavior of our protocol under desired circumstances.
Nevertheless, we agree with Reviewer 1 that more realistic
configurations are of interest. We left this as future work, where we
would like to replace the DHT of IPFS by our protocol, and deploy it
on a real distributed infrastructure.

** About Figure 7 link: We agree with Reviewer 2 that a single
intercontinental link is not realistic, however this allows us
to confirm and highlight the very important property that our
protocol works even in a network with physical partitions. // (TODO) more ?
** About Figure 7 time: We use simulated time as x-axis to highlight that
the convergence speed depends on the simulated latency between links.
** Action: Use both cycle and simulated time as x-axis label.
** About simulated time and real network conditions: we only simulated 
the link latency using event-based PeerSim, i.e., the number of cycles
(simulated milliseconds to help human understanding) between the
sending of a message and its receipt by a neighbor. Other network conditions
such as hardware limitations, packet loss, would indeed increase convergence
time, but we expect it to remain in the same order of magnitude when not catastrophic.
// (TODO) rewrite this…

** Comparison with state-of-the-art: As stated in Related Work,
state-of-the-art approaches have shortcomings that disqualify them as
contender in our context: Centralized and DHT approaches have slow
response time; vector-based routing and replicated stores flood the
whole network; timeout-based, random walks, and spanning forests are
cycle-based which never-endlessly floods the network.

// 582 words [2022-06-01 Mer] 11:58

### 2022-06-02 rebuttal2.txt

We thank the three reviewers for their thorough reading and
interesting comments. We hope that our response will clarify all of
their interrogations.

* About motivation and practical application: (TODO) Add reference to Bastien's paper

Our primer target, as the title states, is distributed content
indexing, and more specifically, its content location
service. "Retrieving a content location may actually take more time
than retrieving the content itself."  As an example, consider Alice
from Europe who wants to download a video. She first needs to know
where to download it from. Therefore, she asks to a content location
service that is unfortunately, centralized, and hosted in Australia.
After a round-trip of messaging, she realizes that she wasted time
since the video, or a replica of it, was next to her in Europe all
along.

One might think that distributing the indexing service in Europe using
DHTs would be sufficient to avoid this pitfall. However, DHTs do not
colocate content and location services. Therefore, despite having a
DHT node in Europe, the one that actually knows where to find the
video is still in Australia. Alice still wastes time.

Content delivery networks (CDN) is most often the solution. However,
it requires a priori configuration. Missconfigured CDN still makes
Alice search for her content location in Australia.

On the opposite, using our approach, the node in Europe automatically
knows its closest content location. When Alice asks for the video, she
asks to the European node that answer her immediately with the video
hosted in Europe.

Our approach is not limited to content indexing, and generalizes to
any replicated service. On a side note, it even constitutes an
efficient way to perform multi-destinations shortest path in dynamic
graphs.

** Action: We agree with Reviewer 1. We add such running example
throughout the paper, thus complementing the text description of
figures, to further help the reader.

* About failure detection: We agree with Reviewer 2 that implementing
link failure detection is often done using heartbeats. Our approach is
built on top of such links and benefits, as many other running
protocols, from such failure detection. Since this is a shared overhead,
we do not account it as being part of our protocol. // (TODO) better wording
** Action: We clarify this requirement and its implication on the overhead.

* About crash recovery: Crashes may have immediate impact
on neighboring nodes depending on their crash detection speed.
Therefore, a node must always restart anew, thus retrieving and
propagating relevant information again.
** Side note: There exists a trade-off between convergence speed and
and generated traffic when buffering incoming messages and only
propagating most relevant ones. We kept this out of scope for the
sake of simplicity.

### 2022-06-02 rebuttal2.md

We thank reviewers for their thorough reading and interesting
comments. We hope that our response will clarify their interrogations.

# Reviewer 1

## Motivation and practical application:
The starting point of our study is about minimizing response time of
locating content in geo-distributed infrastructures. Each time someone
looks for a particular content, it must start by locating it in the
infrastructure: a first node is reached to determine its location and
then, the content is retrieved from a second node [1]. "Retrieving a
content location may actually take more time than retrieving the
content itself".

For instance, let us consider Alice from Vienna who wants to download
a video. She first needs to know where to retrieve it from, and so
asks a content location service. If the latter is centralized and
hosted far away in Australia, the round-trip time to interact with the
location service is detrimental, especially when the video is actually
stored close to Vienna.

One might think that distributing the indexing service using DHTs
would be sufficient to avoid this pitfall. However, DHTs do not
collocate content and location services. Therefore, despite having a
DHT node in Vienna, the one that actually knows where to find the
video Alice is looking for is still in Australia. Hence, the
interaction with the location service is still time-consuming.

Using our approach, each node in charge of maintaining content
locations knows at any time the closest location for a particular
content. This allows Alice to contact its close Vienna location
service to then download the video from her closest location, thus
improving response time.

Our approach is not limited to content indexing, and generalizes to
any replicated service. On a side note, it even constitutes an
efficient way to perform multi-destinations shortest path in dynamic
graphs.

### Action:
Slightly revise the introduction to instantiate this Vienna example
and complement the description of figures to further help the reader.

## Simulations vs emulations vs in-vivo:
PeerSim, despite being old, remains a simple and flexible framework to
run large scale simulations in comparison to Splay, Mininet etc.  It
fits our goal of isolating the behavior of our protocol under desired
circumstances.

We focus our experiments on link latency. Other network conditions
such as hardware limitations and heterogeneity, packet loss, link
congestion, would indeed increase convergence time, but we expect it
to remain in the same order of magnitude when not catastrophic.

Nevertheless, we agree that more realistic configurations are of
interest. We leave this as future work, where we would replace the DHT
of IPFS by AS-cast, and deploy it on a real distributed
infrastructure.

## Comparison against state-of-the-art:
While previous works proposed such comparisons [1], we voluntarily
discard them as they have well-identified shortcomings: Centralized
and DHT approaches do not collocate content and location services,
leading to slow response time; vector-based routing and replicated
stores flood the whole network at each event; timeout-based, random
walks, and spanning forests are cycle-based which never-endlessly
floods (part of) the network.

## Figure 7 time:
The time reported on Figure 7 corresponds to the simulated one. A
cycle is a simulated millisecond.

### Action:
Underline in the legend that every reported time is a simulated one.

# Reviewer 2

## Centralized and DHT
Please, look at the first anwser provided to Reviewer 1.

## Node failures:
Algorithm 3 is designed to handle changes in the infrastructure.
"Removing a node is equivalent to removing all its edges". Therefore,
"What happens if this direct parent fails?": Algorithm 3, line 4
states that this event is equivalent to a possible deletion. The
detecting node must propagate the changes to its neighbors
accordingly.

Regarding the detection of failures, we indeed assume a low level
mechanism, such as heartbeats.  AS-cast is built on top of such a
mechanism, and as many other running protocols, benefits from such
failure detection.

### Action:
We clarify this requirement and its implication on the overhead.

## Scenarios 3e and 5e
Figure 3 illustrates the challenge of maintaining consistent
information.  Figure 5 demonstrates that Node C cannot distinguish the
two scenarios.  The node must assume the worst possible outcome and
propagate delete messages in both cases, that would be true in Figure
3f, but false positives in Figure 5f. AS-cast guarantees that every
node converge to its proper partition afterwards.

## First evaluation practicability
The topology is indeed arbitrary as we do not find any real
geo-distributed topology reaching such a scale of 10K nodes.  We
thought of instantiating multiple times the GEANT topology but
interconnecting them would also be arbitrary.

## About worst-case scenario
Let us consider a chained set of Z nodes [A-Z] and the sequential
creation of partitions, the number of messages in the worst case is:
25×2 + 24×2+ … + 1×2 = O(2×Z^2).

When creating the same partitions in parallel, the number of messages
is only: 2×25.

## Size of packets
We agree that transferred bytes would be of interest, especially to
compare with other approaches in more realistic settings as we plan in
future work.

## Single link between continents
We agree that this scenario is unrealistic; and also that partitions
may span multiple continents. AS-cast would work in such scenario.
This experiment aim to demonstrate that AS-cast behaves correctly in
case of physical partitions. We find this result most interesting
since decentralized protocols often fail to do so.

# Reviewer 3

## Content indexing formal problem 
We chose to abstract the content indexing challenge as a more general
partitioning problem and so formalize it this way (see also first
answer to R1-R2).

## Scope predicate
This is indeed an interesting point. We thank to reviewer for this
valuable remark and let it as future work.

## Black-and-white
### Action:
We agree and make colored figures black-and-white friendly.

## Crash recovery
Crashes may have immediate impact on neighboring nodes.  Therefore, a
node always restart anew, retrieving and propagating relevant
information again.

[1] https://hal.archives-ouvertes.fr/hal-02190125/file/tnsm.pdf

### 2022-06-02 rebuttal2.md

We thank reviewers for their thorough reading and interesting
comments. We hope that our response will clarify their interrogations.

# Reviewer 1

## Motivation and practical application:
Our starting point is about minimizing response time of locating
content in geo-distributed infrastructures. Each time someone looks
for a particular content, a first node is reached to determine its
location and then, the content is retrieved from a second node
[1]. "Retrieving a content location may actually take more time than
retrieving the content itself".

For instance, let us consider Alice from Vienna who wants to download
a video. She first needs to know where to retrieve it from, and so
asks a content location service. If the latter is centralized and
hosted far away in Australia, the round-trip to interact with the
location service is detrimental, especially when the video is actually
stored close to Vienna.

One might think that distributing the indexing service using DHTs
would be sufficient to avoid this pitfall. However, DHTs do not
collocate content and location services. Therefore, despite having a
DHT node in Vienna, the one that actually knows where to find the
video Alice is looking for is still in Australia. Hence, the
interaction with the location service remains time-consuming.

Using AS-cast, each node in charge of maintaining content locations
knows at any time the closest location for a particular content.
Alice contacts her Vienna location service then downloads the video
from her closest host, hence improving quality of service.

AS-cast is not limited to content indexing, and generalizes well to
any replicated service. It even constitutes an efficient way to
perform multi-destinations shortest path in dynamic graphs.

**Action:** Slightly revise the introduction to instantiate this
Vienna example and complement the description of figures to further
help the reader.

@@

## Simulations vs emulations vs in-vivo:
PeerSim, despite being old, remains a simple and flexible framework to
run large scale simulations in comparison to Splay, Mininet etc.  It
fits our goal of isolating the behavior of our protocol under desired
circumstances.

We focus our experiments on link latency. Other network conditions
such as hardware limitations, hardware heterogeneity, packet loss,
link congestion, would indeed increase convergence time, but we expect
it to remain in the same order of magnitude when not catastrophic.

@@

## Comparison against state-of-the-art:
While previous works proposed such comparisons [1], we voluntarily
discard them as they have well-identified shortcomings: Centralized
and DHT approaches do not collocate content and location services,
leading to slow response time; vector-based routing and replicated
stores flood the whole network at each event; timeout-based, random
walks, and spanning forests are cycle-based which never-endlessly
floods (part of) the network.

## Figure 7 time:
The time reported on Figure 7 corresponds to the simulated one. A
cycle is a simulated millisecond.

# Reviewer 2

## Centralized and DHT
Please, read the first anwser provided to Reviewer 1.

## Node failures:
Algorithm 3 handle changes in infrastructures.  "Removing a node is
equivalent to removing all its edges". Therefore, "What happens if
this direct parent fails?": Algorithm 3, line 4 states that this event
is equivalent to a possible source deletion. The detecting node
propagates the changes to its neighbors accordingly.

To detect failures, we indeed assume a low level mechanism, such as
heartbeats. Since many other running protocols benefit from provided
failure detection, we do not consider it as an overhead of our
protocol.

**Action:** Clarify this requirement and the implication on the
overhead.

## Scenarios 3e and 5e
Figure 3 illustrates the challenge of maintaining consistent
information.  Figure 5 shows that Node C cannot distinguish the two
scenarios.  The node assumes the worst outcome and propagates delete
messages in both cases, that would be true in Figure 3f, but false
positives in Figure 5f. AS-cast guarantees that every node converges
to its proper partition afterwards.

## First evaluation practicability
The topology is indeed arbitrary as we do not find any real
geo-distributed topology reaching such a scale of 10K nodes.  We
thought of instantiating GEANT multiple times but this remains
arbitrary.

## About worst-case scenario
Let us consider a chained set of Z nodes [A-Z] and the sequential
creation of partitions, the number of messages is: 25×2 + 24×2+ … +
1×2 = O(2×Z^2).

When creating all partitions in parallel, the number of messages is
only: 2×25.

## Packets size
We agree that transferred bytes would be of interest, especially to
compare with other approaches in more realistic settings as we plan in
future work.

## Single link between continents
We agree that this scenario is unrealistic; and also that partitions
may span multiple continents. AS-cast would work in such scenario.
Nevertheless, this experiment aims to demonstrate that AS-cast behaves
correctly in case of physical partitions. We find this result most
interesting since decentralized protocols often fail in such context.

@@

# Reviewer 3

## Content indexing formal problem 
We chose to abstract the content indexing challenge as a more general
partitioning problem and formalize it this way (see also first answer
to Reviewer 1).

## Scope predicate
We agree that predicates need another constraint to qualify the
broadcast as scoped broadcast. Although we leave this as future work.

## Black-and-white
**Action:** We agree and make colored figures black-and-white
friendly.

## Crash recovery
Crashes may have immediate impact on neighboring nodes.  Therefore,
nodes always restart anew, retrieving and propagating relevant
information again.

### 2022-06-02 rebuttal2.md

We thank reviewers for their thorough reading and interesting
comments. We hope that our response will clarify their interrogations.

# Reviewer 1

## Motivation and applications:
Our starting point is about minimizing response time of locating
content in geo-distributed infrastructures. When looking for a
content, a first node is reached to determine its location and then,
the content is retrieved from a second node [1]. "Retrieving a content
location may actually take more time than retrieving the content
itself".

For instance, let us consider Alice from Vienna who wants to download
a video. She must know where to retrieve it from, therefore she asks a
content location service. If the latter is centralized and hosted far
away in Australia, the round-trip with the service is detrimental,
especially when the video is actually stored close to Vienna.

Distributing the indexing service using DHTs is insufficient to avoid
this pitfall: DHTs do not collocate content and location
services. Therefore, despite having a DHT node in Vienna, the one that
actually knows where to find the video Alice is looking for is still
in Australia. Interacting with the location service remains
time-consuming.

Using AS-cast improves quality of service since each node in charge of
maintaining content locations knows at any time the closest location
for a particular content.  Alice contacts her Vienna location service
then downloads the video from her closest host.

@@

AS-cast is not limited to content indexing, and generalizes well to
any replicated service. It even constitutes an efficient way to
perform multi-destinations shortest path in dynamic graphs.

**Action:** Slightly revise the introduction to instantiate this
Vienna example and complement figure descriptions to further help the
reader.

@@

## Simulations vs emulations vs in-vivo:
PeerSim, despite being old, remains a simple and flexible framework to
run large scale simulations in comparison to Splay, Mininet etc.  It
fits our goal of isolating the behavior of our protocol under desired
circumstances.

We focus our experiments on link latency. Other network conditions
such as hardware limitations/heterogeneity, packet loss,
link congestion, would indeed increase convergence time, but we expect
it to remain in the same order of magnitude when not catastrophic.

Nevertheless, we agree that more realistic configurations are of
interest. We leave this as future work: replace the DHT of IPFS by
AS-cast, and deploy it on a real distributed infrastructure.

## State-of-the-art comparison:
Previous works proposed such comparisons [1]. We discard them as they
have well-identified shortcomings: Centralized and DHT approaches do
not collocate content and location services, leading to slow response
time; vector-based routing and replicated stores flood the whole
network at each event; timeout-based, random walks, and spanning
forests are cycle-based which never-endlessly floods (parts of) the
network.

@@

## Figure 7 time:
The time reported on Figure 7 corresponds to the simulated one. A
cycle is a simulated millisecond.

# Reviewer 2

## Centralized and DHT
Please, read the first anwser provided to Reviewer 1.

## Node failures:
Algorithm 3 handles infrastructure changes.  "Removing a node is
equivalent to removing all its edges". Therefore, "What happens if
this direct parent fails?": Algorithm 3, line 4 triggers a *possible*
source deletion. The detecting node propagates the changes to its
neighbors accordingly.

@@

To detect failures, we indeed assume a low level mechanism, such as
heartbeats. Since many other running protocols benefit from provided
failure detection, we do not consider it as an overhead of our
protocol.

**Action:** Clarify this requirement and the implication on the
overhead.

## Scenarios 3e and 5e
Figure 3 illustrates the challenge of maintaining consistent
information.  Figure 5 highlights the challenge that Node C cannot
distinguish the two scenarios.  The node assumes the worst and
propagates delete messages in both cases, rightfully in Figure 3f,
wrongfully in Figure 5f. Afterwards, AS-cast ensures that every node
converges to the correct partition.

## First evaluation practicability
The topology is indeed arbitrary as we do not find any real
geo-distributed topology reaching 10K nodes.  Instantiating GEANT
multiple times would remain arbitrary.

## Worst-case scenario
Let us consider Z chained nodes [A->Z] and a sequential creation of
partitions, the number of messages is: 25×2 + 24×2 +…+ 1×2 =
O(2×Z^2).

@@

When creating all partitions in parallel, the number of messages is
only: 2×25.

## Packets size
We agree that transferred bytes would be interesting, especially to
compare with other approaches in realistic settings as we plan in
future work.

## Single link between continents
We agree that this scenario is unrealistic.  Nevertheless, this
experiment aims to demonstrate that AS-cast behaves correctly in case
of physical partitions. We find this result most interesting since
decentralized protocols often fail in such context.

@@

# Reviewer 3

## Content indexing problem 
We chose to abstract the content indexing challenge as a more general
partitioning problem and formalize it this way.

## Scope predicate
We advocate that any predicate would work: the scope of an always true
predicate would simply be "all nodes".

## Black-and-white
**Action:** Make figures black-and-white friendly.

### 2022-06-03 rebuttal2.md

We thank reviewers for their thorough reading and interesting
comments. We hope that our response will clarify their interrogations.

# Reviewer 1

## Motivation and applications:
Our starting point is about minimizing response time of locating
content in geo-distributed infrastructures. When looking for a content,
a node is reached to determine its location and then, the content is
retrieved from another node [1]. __"Retrieving a content location may
actually take more time than retrieving the content itself"__.

Let us consider Alice from Vienna who wants to download a video. She
must know where to retrieve it from, therefore she asks a content
location service. If the latter is centralized and hosted faraway in
Australia, the round-trip to the service is detrimental, especially
when the video is actually stored close to Vienna.

Distributing indexing services using DHTs is insufficient to avoid
this pitfall: DHTs do not collocate content and location
services. Therefore, despite having a DHT node in Vienna, the one that
actually knows where to find the video Alice is looking for is still
in Australia. Interacting with the location service remains
time-consuming.

AS-cast improves quality of service since each node in charge of
maintaining content locations always knows the closest location for a
particular content.  Alice contacts her Vienna location service then
downloads the video from her closest host.

@@

AS-cast is not limited to content indexing, and generalizes well to
any replicated service. It even constitutes an efficient way to
perform multi-destinations shortest path in dynamic graphs.

**Action:** Slightly revise the introduction to instantiate this
Vienna example and complement figure descriptions.

## Simulations vs emulations vs in-vivo:
PeerSim remains a simple and flexible framework to run large scale
simulations in comparison to Splay, Mininet etc.  It fits our goal of
isolating the behavior of our protocol under desired circumstances.

We focus our experiments on link latency. Other network conditions
such as hardware limitations/heterogeneity, packet loss, link
congestion, would indeed increase convergence time, but we expect an
identical order of magnitude when not catastrophic.

@@

## State-of-the-art comparison:
Previous works proposed such comparisons [1]. We discard them as they
have well-identified shortcomings: Centralized and DHT approaches do
not collocate content and location services, leading to slow response
time; vector-based routing and replicated stores flood the whole
network at each event; timeout-based, random walks, and spanning
forests are cycle-based which never-endlessly floods (parts of) the
network.

## Figure 7 time:
The time reported on Figure 7 corresponds to the simulated one. A
cycle is a simulated millisecond.

# Reviewer 2

## Centralized and DHT
Please, read the first answer provided to Reviewer 1.

## Node failures:
Algorithm 3 handles infrastructure changes.  __"Removing a node is
equivalent to removing all its edges"__.  Therefore, "What happens if
this direct parent fails?": Algorithm 3, line 4 triggers a _possible_
source deletion. The detecting node propagates the changes to its
neighbors accordingly.

@@

To detect failures, we indeed assume a low level mechanism, such as
heartbeats. Since many other running protocols benefit from provided
failure detection, we do not consider it as an overhead of our
protocol.

**Action:** Clarify requirements and overhead implications.

## Scenarios 3e and 5e
Figure 3 illustrates the challenge of maintaining consistent
information.  Figure 5 highlights the challenge that Node C cannot
distinguish the two scenarios.  The node assumes the worst and
propagates delete messages in both cases, rightfully in Figure 3f,
wrongfully in Figure 5f. Afterwards, AS-cast ensures that every node
converges to its correct partition.

@@

## First evaluation practicability
The topology is indeed arbitrary as we do not find any real
geo-distributed topology reaching 10K nodes.  Instantiating GEANT
multiple times would remain arbitrary.

## Worst-case scenario
Let us consider [A..Z] chained nodes, and a sequential creation of
partitions, the number of messages is: 25×2 + 24×2 +…+ 1×2 = O(2×Z^2).
Whereas in parallel, the number of messages is only: 2×25.

@@

## Packets size
We agree that transferred bytes would be interesting, especially to
compare with other approaches in realistic settings as we plan in
future work.

## Intercontinental link
We agree that this scenario is unrealistic.  Nevertheless, this
experiment aims to demonstrate that AS-cast behaves correctly in case
of physical partitions. We find this result most interesting since
decentralized protocols often fail in such context.

@@

# Reviewer 3

## Content indexing problem 
We chose to abstract the content indexing challenge as a more general
partitioning problem and formalize it this way.

## Scope predicate
Any predicate would work: the scope of an always true predicate would
trivially be "all nodes".

@@

## Black-and-white
**Action:** Make figures black-and-white friendly.

## Crash recovery
Crashes may impact neighboring nodes immediately.  Therefore,
nodes always restart anew, retrieving and propagating relevant
information again.

### 2022-06-03 rebuttal2.md

AS-cast improves quality of service since each node in charge of
maintaining content locations always knows the closest location for a
particular content.  Alice contacts her Vienna location service then
downloads the video from her closest host.

AS-cast is not limited to content indexing, and generalizes well to
any replicated service. It even constitutes an efficient way to
perform multi-destinations shortest path in dynamic graphs.

**Action:** Slightly revise the introduction to instantiate this
Vienna example and complement figure descriptions.

## Simulations vs emulations vs in-vivo:
PeerSim, despite being old,  remains a simple and flexible framework to 
run large scale simulations in comparison to Splay, Mininet etc.  It 
fits our goal of isolating the behavior of our protocol simulating link latencies.

Other network conditions such as hardware diversity,  packet loss, congestion, would indeed increase convergence time, but we expect an
identical order of magnitude when not catastrophic.

Nevertheless, we agree more realistic configurations are of
interest. We leave this as future work by revising IPFS by
AS-cast, and deploy it on a real infrastructure.

### 2022-06-03 rebuttal2.md

We thank reviewers for their thorough reading and interesting
comments. We hope that our response will clarify their interrogations.

# Reviewer 1

## Motivation and applications:
Our starting point is about minimizing response time of locating
content in geo-distributed infrastructures. When looking for a
content, a node is reached to determine its location, then, the
content is retrieved from another node [1]. _"Retrieving a content
location may actually take more time than retrieving the content
itself"_.

Consider Alice from Vienna who wants to download a video. She must
know where to retrieve it from, therefore she asks a content location
service. If the latter is centralized and hosted faraway in Australia,
the round-trip to the service is detrimental, especially when the
video is actually stored close to Vienna.

Distributing location services using DHTs is insufficient: DHTs do not
collocate content and location services. Therefore, despite having a
DHT node in Vienna, the one that knows where to find the video Alice
is looking for may still be in Australia. Interacting with the service
remains time-consuming.

AS-cast improves QoS since every node maintaining content locations
always knows its closest location for a particular content.  Alice
contacts her Vienna location service then downloads the video from her
closest host.

@@

AS-cast is not limited to content indexing, and generalizes well to
any replicated service. It even constitutes an efficient way to
perform multi-destinations shortest path in dynamic graphs.

**Action:** Slightly revise Introduction using this example and
complement figure descriptions.

## Simulations vs emulations vs in-vivo:
PeerSim remains a flexible framework to run large scale
simulations. It fits our goal of isolating our protocol's behavior
under desired circumstances.

Experiments focus on link latency. Other network conditions (hardware
limitations/heterogeneity, loss, congestion…) would indeed increase
convergence time, but we expect an identical order of magnitude when
not catastrophic.

Nevertheless, we agree that more realistic configurations are of
interest. We leave this as future work: replace IPFS's DHT by AS-cast,
and deploy on real distributed infrastructures.

## State-of-the-art comparison:
Previous works proposed such comparisons [1]. We discard them as they
have well-identified shortcomings: Centralized and DHT approaches do
not collocate content and location services, leading to slow response
time; vector-based routing and replicated stores flood the network at
each event; timeout-based, random walks, and spanning forests are
cycle-based which never-endlessly floods the network.

## Figure 7 time:
The time reported on Figure 7 is the simulated one. A cycle is a
simulated millisecond.

@@

# Reviewer 2

## Centralized and DHT
Please, read the first answer provided to Reviewer 1.

## Node failures:
Algorithm 3 handles infrastructure changes.  _"Removing a node is
equivalent to removing all its edges"_.  Therefore, "What happens if
this direct parent fails?": Algorithm 3, line 4 triggers a _possible_
source deletion. The detecting node propagates the changes to its
neighbors accordingly.

To detect failures, we indeed assume a low level mechanism
(eg. heartbeats). Since many other running protocols benefit from it,
we do not consider it an overhead of AS-cast.

@@

**Action:** Clarify requirements and overhead implications.

## Scenarios 3e and 5e
Figure 3 illustrates the challenge of consistency.  Figure 5
highlights the *challenge* that Node C *cannot* distinguish the two
scenarios.  The node assumes the worst and propagates delete messages:
rightfully in Figure 3f, wrongfully in Figure 5f. Afterwards, AS-cast
still ensures convergence.

@@

## First evaluation practicability
The topology is indeed arbitrary as we do not find any real
geo-distributed topology reaching 10K nodes.  Instantiating GEANT
multiple times would remain arbitrary.

## Worst-case scenario
Consider [A..Z] chained nodes, and a sequential creation of
partitions, the number of messages is: 25×2 + 24×2 +…+ 1×2 = O(2×Z^2).
Whereas in parallel, the number of messages is only: 2×25.

@@

## Packets size
We agree that transferred bytes would be interesting, especially to
compare with other approaches in realistic settings as we plan in
future work.

## Intercontinental link
We agree that this scenario is unrealistic.  Nevertheless, this
experiment aims to demonstrate that AS-cast behaves correctly when
physical partitions occur. We find this result most interesting since
decentralized protocols often fail in such context.

### 2022-06-24 input/introduction.tex
minors
quick format

The data storage paradigm shifted from centralized in
the cloud to distributed at the edges of the network. 
% There is an ongoing evolution of storing data from the cloud to the
% edges of the network.
This change aims at keeping the data close to
\begin{inparaenum}[(i)]
\item its producers since data may be too expensive or sensitive to be
  transmitted through the network; and
\item its consumers so data may quickly and efficiently reach
  them~\cite{cachier, foggy_cache, shi2016edge}.
\end{inparaenum}
%% It avoids transmitting Either because it is where it has been
%% created and it is too expensive to be transmitted through the
%% network, or because it has been replicated to bring data closer to
%% the end users ~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, new designs for data management across Edge
infrastructures have been investigated~\cite{confais2017object,
  confais2017performance, fogstore, hasenburg2020towards}.  They
enable strategies to confine traffic by writing data locally and
replicating content according to effective needs. However, locating
content remains challenging. Retrieving a content location may
actually take more time than retrieving the content itself.
%% Although
%% these systems, provide good properties such as favouring network
%% traffic confinement by writting data locally and replicating contents
%% according to the effective needs, determining the location where to
%% get the content might be more expensive than retrieving the content
%% itself.
%
Indeed, these systems, when not using a centralized index hosted in a
Cloud, rely on \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT) spread across different \processes composing
the infrastructure~\cite{maymounkov2002kademlia}. When a client wants
to access specific content, it requests a remote \process to provide
at least one \process identity to retrieve this content from. After
retrieving the content, the client can create another replica to
improve the performance of future accesses, but it must recontact the
indexing service to notify of the creation of this new replica.
%% a local replica is created to improve the performance for future
%% accesses and the process in charge of maintaining the index is
%% contacted once again to reflect this new location.
%

@@

Such approaches are in contradiction with the objectives of Edge
infrastructures that aim at reducing the impact of latency as well as
the volume of data passing through the network.
%
First, accessing a remote \node to request content location(s) raises
hot spots and availability issues. But most importantly, it results in
additional delays~\cite{asrese2019measuring, doan2019tracing} that
occur even before the actual download started.
%
Second, the client gets a list of content locations at the discretion
of content indexing services. Without information about these
locations, it often ends up downloading from multiple replica hosts,
yet only keeping the fastest answer. In turn, clients either waste
network resources, or face lower response time.
%% there is no information to select the ``best'' node among the
%% possible candidates from which the content could be retrieved. In
%% most cases, this results in parallel requests performed by the
%% client node to each candidate with the goal of retrieving the
%% content as efficient as possible.

To address the aforementioned limitations, every \process that might
request or replicate content must also host its own content indexing
service in a fully decentralized fashion~\cite{kermarrec2015want}. At
any time, it can immediately locate the closest replica of specific
content.  A naive approach would be that every \process indexes and
ranks \emph{every live} replica along with its \emph{location}
information. When creating or destroying a replica, a \process would
notify all other \processes by broadcasting its
operation~\cite{birman1999bimodal, hadzilacos1994modular}. Unfortunately, this also contradicts Edge
infrastructure objectives, for such a protocol does not confine the
traffic generated to maintain its indexes. A \process may acknowledge
the existence of replicas at the other side of the network while there
already exists a replica next to it.

@@

>>>>

The data storage paradigm shifted from centralized in
the cloud to distributed at the edges of the network. 
% There is an ongoing evolution of storing data from the cloud to the
% edges of the network.
This change aims at keeping the data close to
\begin{inparaenum}[(i)]
\item its producers since data may be too expensive or sensitive to be
  transmitted through the network; and
\item its consumers so data may quickly and efficiently reach
  them~\cite{cachier,foggy_cache,shi2016edge}.
\end{inparaenum}
%% It avoids transmitting Either because it is where it has been
%% created and it is too expensive to be transmitted through the
%% network, or because it has been replicated to bring data closer to
%% the end users ~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, new designs for data management across Edge
infrastructures have been investigated~\cite{confais2017object,confais2017performance,fogstore,hasenburg2020towards}.  They
enable strategies to confine traffic by writing data locally and
replicating content according to effective needs. However, locating
content remains challenging. Retrieving a content location may
actually take more time than retrieving the content itself.
%% Although
%% these systems, provide good properties such as favouring network
%% traffic confinement by writting data locally and replicating contents
%% according to the effective needs, determining the location where to
%% get the content might be more expensive than retrieving the content
%% itself.
%
Indeed, these systems, when not using a centralized index hosted in a
Cloud, rely on \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT) spread across different \processes composing
the infrastructure~\cite{maymounkov2002kademlia}. When a client wants
to access specific content, it requests a remote \process to provide
at least one \process identity to retrieve this content from. After
retrieving the content, the client can create another replica to
improve the performance of future accesses, but it must recontact the
indexing service to notify of the creation of this new replica.
%% a local replica is created to improve the performance for future
%% accesses and the process in charge of maintaining the index is
%% contacted once again to reflect this new location.
%

@@

Such approaches are in contradiction with the objectives of Edge
infrastructures that aim at reducing the impact of latency as well as
the volume of data passing through the network.
%
First, accessing a remote \node to request content location(s) raises
hot spots and availability issues. But most importantly, it results in
additional delays~\cite{asrese2019measuring,doan2019tracing} that
occur even before the actual download started.
%
Second, the client gets a list of content locations at the discretion
of content indexing services. Without information about these
locations, it often ends up downloading from multiple replica hosts,
yet only keeping the fastest answer. In turn, clients either waste
network resources, or face slower response time.
%% there is no information to select the ``best'' node among the
%% possible candidates from which the content could be retrieved. In
%% most cases, this results in parallel requests performed by the
%% client node to each candidate with the goal of retrieving the
%% content as efficient as possible.

To address the aforementioned limitations, every \process that might
request or replicate content must also host its own content indexing
service in a fully decentralized fashion~\cite{kermarrec2015want}. At
any time, it can immediately locate the closest replica of specific
content.  A naive approach would be that every \process indexes and
ranks \emph{every live} replica along with its \emph{location}
information. When creating or destroying a replica, a \process would
notify all other \processes by broadcasting its
operation~\cite{birman1999bimodal,hadzilacos1994modular}. Unfortunately, this also contradicts Edge
infrastructure objectives, for such a protocol does not confine the
traffic generated to maintain its indexes. A \process may acknowledge
the existence of replicas at the other side of the network while there
already exists a replica next to it.

@@

%% Ultimately, \NAME can constitute a novel building block for
%% geo-distributed services in need of efficient resource sharing in the
%% vicinity of regions. For instance, AS-cast could complement content
%% delivery infrastructures~\cite{triukose2011measuring} by efficiently
%% sharing between nodes attached to the same CDN server the locations of
%% web objects that have already been downloaded.  \NAME could even
%% constitute a decentralized implementation solving the multiple
%% destinations shortest path problem.
